Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-13 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Latex corrections

The basic Rastrigins function is separable[], and is defined as follows;
\begin{equation}
F_{rastrigin}(x)=\sum\limits_{i=1}^\frac{D} [x_{i}^{2}-10\cos(2\pi x_i)+10  ] 
\end{equation}
where $D$ is the dimension and $x = (x1, x2, · · · , x_{D})$ is a
$D$-dimensional row vector (i.e., a $1 × D$ matrix). Rastrigin’s function 
is a classical multimodal problem. It is difficult since the number of local
optima grows exponentially with the increase of dimensionality. To make it 
nonseparable, an orthogonal matrix is also used for coordinate rotation.
The rotated Rastrgin’s function is defined as follows:
\begin{equation}
F_{rot_rastrigin}(x)=F_{rastrigin}(\textbf{z}), \textbf{z}= \textbf{x} * \textbf{M}
\end{equation}
Where \textbf{M}_{is} a $D×D$ orthogonal matrix.

The benchmark  emulates real-world optimization problems that most likely will consist 
of different groups of parameters with strong dependencies within
but little interaction between the groups. This issue is reflected in the benchmark
problems by first randomly dividing the objective variables
into several groups, each of which contains a number of variables. The parameter $m$ 
is used to control the number of variables in each group and hence, defining the degree
of separability:
\begin{equation}
F_{15}(x)=\sum\limits_{k=1}^\frac{D}{m}F_{rot_rastrigin}[\textbf{z}(F_{(k-1)*m+1}:P_{k*m})] 
\end{equation}
For the benchmark $D = 1000$, Group size $m = 50$, $\textbf{x} = (x_1, x_2, · · · , x_{D})$ is the
candidate solution, $\textbf{o} = (o_1, o_2, · · · , o_{D})$ is the shifted global optimum,
$\textbf{z} = \textbf{x} − \textbf{o}$ is the shifted candidate solution and
finally $\textbf{P}$ is a random permutation of ${1, 2, · · · ,D}$.
%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

>>>>

The basic Rastrigins function is separable[], and is defined as follows;
\begin{equation}
F_{rastrigin}(x)=\sum\limits_{i=1}^D [ x_{i}^{2}-10\cos(2\pi x_i)+10  ] 
\end{equation}
where $D$ is the dimension and $x = (x1, x2, · · · , x_{D})$ is a
$D$-dimensional row vector (i.e., a $1 × D$ matrix). Rastrigin’s function 
is a classical multimodal problem. It is difficult since the number of local
optima grows exponentially with the increase of dimensionality. To make it 
nonseparable, an orthogonal matrix is also used for coordinate rotation.
The rotated Rastrgin’s function is defined as follows:
\begin{equation}
F_{rot\_rastrigin}(x)=F_{rastrigin}(\textbf{z}), \textbf{z}= \textbf{x} * \textbf{M}
\end{equation}
Where $\textbf{M}$ is  a $D \times{D}$ orthogonal matrix. The benchmark
emulates real-world optimization problems that most likely will consist 
of different groups of parameters with strong dependencies within
but little interaction between the groups. This issue is reflected in the benchmark
problems by first randomly dividing the objective variables
into several groups, each of which contains a number of variables. The parameter $m$ 
is used to control the number of variables in each group and hence, defining the degree
of separability:
\begin{equation}
F_{15}(x)=\sum\limits_{k=1}^\frac{D}{m}F_{rot\_rastrigin}[\textbf{z}(P_{(k-1)*m+1}:P_{k*m})] 
\end{equation}
For the benchmark $D = 1000$, Group size $m = 50$, $\textbf{x} = (x_1, x_2, \ldots , x_{D})$ is the
candidate solution, $\textbf{o} = (o_1, o_2, \ldots  , o_{D})$ is the shifted global optimum,
$\textbf{z} = \textbf{x} - \textbf{o}$ is the shifted candidate solution and
finally $\textbf{P}$ is a random permutation of $\lbrace1, 2, \ldots  ,D\rbrace$.
%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
